Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-04 paper.tex
Add details about benchmark tests.

The motion planning algorithms presented in this paper have been implemented
using KineoWorks\texttrademark \cite{laumond2006kcs}. The planning times have been measured
on an Intel Core~2~Duo 2.13~GHz PC with 2~GB of RAM. Evaluation of the
randomized algorithm has been conducted by executing 50 trials on each
of the first two problems. We present the average results of these trials.

>>>>

\textbf{The motion planning algorithms presented in this paper have been
implemented using KineoWorks\texttrademark \cite{laumond2006kcs}. The
planning times have been measured on an Intel Core~2~Duo 2.13~GHz PC
with 2~GB of RAM. Evaluation of the randomized algorithm has been
conducted by executing 500 trials on each scenario using two flavors of
RRT: the classic RRT and IPP-RRT \cite{FERR04A}. We present the
results in Fig. \ref{fig:rrt-it}, \ref{fig:rrt-t}, \ref{fig:rrt-n}, as
well as in Extension 4 for the raw data.}
